Memory-Efficient Mixed-Precision Implementations for\\Robust Explicit MPC

### 2019-04-10 emsoft-2019/Cont_Syn.tex
edits and comments for section 4
comments on section 5

\section{Controller Synthesis}
\eva{How we actually get the controller, including feedback loop and mixed-precision tuning}
%In this work we present an innovative method for the off-line design (explicit) of robust MPC controllers for linear time invariant systems.
We need to solve the two inequalities in (\ref{eq:delta}) (\ref{eq:quantizationlines}) in order to build a controller with guarantees of robustness.
%The equation for $\varepsilon$ in (\ref{eq:epsilontot}),  contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ that is the error generated from the quantization of hyperplanes $\mathcal{R}$ in a finite number of bits.
%This $\varepsilon_{Q}$ can be tuned based on memory availability in the micro-controller.
%The rule for $\varepsilon_{Q}$ is the following:
%\begin{equation}\label{eq:quantizationlines}
%\varepsilon_{Q} > (H-\hat{H}_{p})\qstatevar+(K-\hat{K}_{p})
%\end{equation}
%This inequality assures that the distance between any hyperplane represented in infinite precision (H and K), and its counter-part quantized in p bits ($(\hat{H})_{p}$ and $(\hat{K})_{p}$), is bounded by $\varepsilon_{Q}$. 
We use Daisy to solve inequality (\ref{eq:quantizationlines}) with respect to p: we assign an arbitrary value to $\varepsilon_{Q}$ and find the minimal-precision p such that the inequality holds. The main advantage of using this approach (compared to fixing the precision p a priori), is that the value for $\varepsilon_{Q}$ can be regulated based on micro-controller specifications (e.g. memory availability).
%To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for finite precision expressions, ables to provide a sound upper-bound to the maximal approximation error of a formula with respect to its real (infinite precision) counterpart. Since the magnitude of the round-off error depends on the range of input variables, any variable encoded in Daisy has to be bounded.
In a similar way, we solve the inequality in (\ref{eq:delta}) with respect to p:
\begin{flalign}
\label{eq:deltaminusmax}
&delta - \Big(\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}|\Big)>=\\
& \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
\end{flalign}

@@

\subsection{Algorithm}
In Listing \ref{lst:alg} we describe the procedure used to design a robust MPC controller such that (\ref{eq:deltaminusmax}) is satisfied.

\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,escapeinside={(*}{*)},caption=design of robust MPC with precision tuning,label={lst:alg}]
 delta = input()
 (*$\varepsilon_{Q}$*) = input()
 assert (delta >= 0 and (*$\varepsilon_{Q}$*) > 0)
 (*$\varepsilon$*) = (*$\varepsilon_{A/D}$*) + (*$\varepsilon_{Q}$*)

 while True:
   (*\maxUij*) = design_robust_MPC(delta, (*$\varepsilon$*))
   if delta > (*\maxUij*):
     (*$err_{max}(u_{i})_{p}$*) = delta-(*\maxUij*)
     UNI_MIX_precision(F, G, (*$err_{max}(u_{i})_{p}$*))
     UNI_MIX_precision(H, K, (*$\varepsilon_{Q}$*))
     break
   else:
     delta=(*\maxUij*)+(*$\varepsilon_{SAFE}$*)
\end{lstlisting}

>>>>

%!TEX root = main.tex
\section{Controller Synthesis}\label{sec:Controller_Synthesis}

\begin{figure}
\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,escapeinside={(*}{*)},basicstyle=\small\ttfamily]
 delta = input()
 (*$\varepsilon_{Q}$*) = input()
 assert (delta >= 0 and (*$\varepsilon_{Q}$*) > 0)
 (*$\varepsilon$*) = (*$\varepsilon_{A/D}$*) + (*$\varepsilon_{Q}$*)

 while True:
   (*\maxUij*) = design_robust_MPC(delta, (*$\varepsilon$*))
   if delta > (*\maxUij*):
     (*$err_{max}(u_{i})_{p}$*) = delta-(*\maxUij*)
     UNI_MIX_precision(F, G, (*$err_{max}(u_{i})_{p}$*))
     UNI_MIX_precision(H, K, (*$\varepsilon_{Q}$*))
     break
   else:
     delta=(*\maxUij*)+(*$\varepsilon_{SAFE}$*)
\end{lstlisting}
\caption{design of robust MPC with precision tuning}
\label{lst:alg}
\end{figure}

\eva{The algorithm in \autoref{lst:alg} needs to be fixed:
\begin{itemize}
  \item Use the math symbol for Delta to be consistent with the rest of the paper
  \item the function design\_robust\_MPC seems to do a lot more than just designing
    the controller, i.e. it seems to return an error bound instead of a controller.
    Split into more steps.
  \item \maxUij and $err_{max}(u_{i})_{p}$ are not good variable names, use a proper variable name
  \item UNI\_MIX\_precision should also be renamed to something more helpful, e.g. tune\_precision?
\end{itemize}
}

In the previous section, we assumed a given precision $p$. In this section we
present our algorithm for deriving a suitable value of $p$ fully automatically.

\subsection{Algorithm}
\eva{This section needs to structure the explanation in the order in which it
appears in the algorithm (i.e. starting from the input and explaining why for
instance $\epsilon_Q$ is an input), and should reference the lines in the
algorithm, not only the equations from the previous section}

\eva{The precision tuning, which is the main contribution of the paper is not explained.}

\subsection{Implementation}
\eva{Some notes about how this is implemented}

\eva{Below is the previous text:}
%In this work we present an innovative method for the off-line design (explicit) of robust MPC controllers for linear time invariant systems.
We need to solve the two inequalities in (\ref{eq:delta}) (\ref{eq:quantizationlines}) in order to build a controller with guarantees of robustness.
%The equation for $\varepsilon$ in (\ref{eq:epsilontot}),  contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ that is the error generated from the quantization of hyperplanes $\mathcal{R}$ in a finite number of bits.
%This $\varepsilon_{Q}$ can be tuned based on memory availability in the micro-controller.
%The rule for $\varepsilon_{Q}$ is the following:
%\begin{equation}\label{eq:quantizationlines}
%\varepsilon_{Q} > (H-\hat{H}_{p})\qstatevar+(K-\hat{K}_{p})
%\end{equation}
%This inequality assures that the distance between any hyperplane represented in infinite precision (H and K), and its counter-part quantized in p bits ($(\hat{H})_{p}$ and $(\hat{K})_{p}$), is bounded by $\varepsilon_{Q}$. 
We use Daisy to solve inequality (\ref{eq:quantizationlines}) with respect to p: we assign an arbitrary value to $\varepsilon_{Q}$ and find the minimal-precision p such that the inequality holds. The main advantage of using this approach (compared to fixing the precision p a priori), is that the value for $\varepsilon_{Q}$ can be regulated based on micro-controller specifications (e.g. memory availability).
%To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for finite precision expressions, ables to provide a sound upper-bound to the maximal approximation error of a formula with respect to its real (infinite precision) counterpart. Since the magnitude of the round-off error depends on the range of input variables, any variable encoded in Daisy has to be bounded.
In a similar way, we solve the inequality in (\ref{eq:delta}) with respect to p:
\begin{flalign}
\label{eq:deltaminusmax}
&delta - \Big(\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}|\Big)>=\\
& \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
\end{flalign}

@@

In Listing \ref{lst:alg} we describe the procedure used to design a robust MPC controller such that (\ref{eq:deltaminusmax}) is satisfied.
